Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-09-26 manuscript/manuscript.tex
Fixed typo
Started writing "Example with real data"

\title[Variable Density Tesseroids]{
    Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth
}
\author[S.R. Soler, L. Uieda and M.E. Gimenez]{
    Santiado R. Soler$^{1,2}$, Leonardo Uieda$^3$ and Mario E. Gimenez$^{1,2}$ \\
    $^1$CONICET, Argentina. e-mail: santiago.r.soler@gmail.com\\
    $^2$Instituto Geofísico Sismológico Volponi, Universidad Nacional de San Juan, Argentina\\
    $^3$Universidade do Estado do Rio de Janeiro, Rio de Janeiro, Brazil
    }

@@

From these results We can conclude that the homogeneous density code is up to twice faster than the new variable density algorithm for lower heights. However, the computation times ratio gets lower at greater heights, due to the reduction of the divisions made by the adaptive discretization algorithm. In summary, the new variable density code is fast enough to perform the calculations of a real model in a few minutes. \todo{real, esta bien la expresion?}

@@

>>>>

\title[Variable Density Tesseroids]{
    Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth
}
\author[S.R. Soler, A. Pesce, L. Uieda and M.E. Gimenez]{
    Santiado R. Soler$^{1,2}$, Agustina Pesce$^{1,2}$, Leonardo Uieda$^3$ and Mario E. Gimenez$^{1,2}$ \\
    $^1$CONICET, Argentina. e-mail: santiago.r.soler@gmail.com\\
    $^2$Instituto Geofísico Sismológico Volponi, Universidad Nacional de San Juan, Argentina\\
    $^3$Universidade do Estado do Rio de Janeiro, Rio de Janeiro, Brazil
    }

@@

From these results we can conclude that the homogeneous density code is up to twice faster than the new variable density algorithm for lower heights. However, the computation times ratio gets lower at greater heights, due to the reduction of the divisions made by the adaptive discretization algorithm. In summary, the new variable density code is fast enough to perform the calculations of a real model in a few minutes. \todo{real, esta bien la expresion?}

@@

\section{Example with real data}

Besides all the tests we have carried out on the new code, we intend to show a forward modelling example with real data.
In order to do that we have chosen the Neuquen Basin: a sedimentary basin located to the east of the Andes, between 32$^\circ$S and 40$^\circ$S latitude (see Figure \ref{fig:neuquen-basin}a), that includes continental and marine siliciclastics, carbonates and evaporites accumulated over the Jurassic and the Cretaceous constituting a stratigraphic record up to 5000m of depth \citep{Howell2005}.

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/neuquen-basin.pdf}
\caption{(a) Topography of Neuquen Basin (in km),
         (b) Thickness of the sedimentary basin (in meters),
         (c)-(h) Computed gravity fields: potential $V$ (in J/kg), gradient components $g_x$, $g_y$ and $g_z$ (in mGal) and Marussi tensor components $g_{xy}$ and $g_{zz}$ (in Eötvös), calculated at 50km of height over the ellipsoid.}
\label{fig:neuquen-basin}
\end{figure*}

The thickness of the sediment pack was obtained from \citet{Heine2007}, which can be seen in Figure \ref{fig:neuquen-basin}.
